---
title: "surgery times"
output:
  pdf_document: default
  html_document: default
date: "2023-09-18"
---

```{r setup, include=FALSE}
install.packages("tidyverse")
library(tidyverse)
```

```{r}
library(dplyr)
surgery_times<- read.csv("surgery_times.csv")
```

## R Markdown
1. What is the average time these encouters occur? 
```{r surgery_times_modification}

surgery_updated<-surgery_times%>%
  mutate(hours_from_6pm = ifelse(hour<=6, hour+6, hour-18))%>%
  filter(hours_from_6pm>0)

surgery_updated
```

```{r}
surgery_updated%>%
  filter(hours_from_6pm<0)
```

```{r}

ggplot(data=surgery_updated, mapping=aes(x=hours_from_6pm))+geom_histogram()
  
)
```

```{r}
mean(surgery_updated$hours_from_6pm)
summary(surgery_updated$hours_from_6pm)
```


Is there an evidence of difference between two hospitals? 

```{r}

summary(surgery_updated%>% filter(hospital == 'A') %>% .$hours_from_6pm)

summary(surgery_updated%>% filter(hospital == 'B') %>% .$hours_from_6pm)

```

```{r}
ggplot(surgery_updated, aes(hospital, hours_from_6pm)) +
        geom_boxplot()
```


```{r}
t.test(hours_from_6pm ~ hospital, data = surgery_updated)
```

2. Controlling for hospital, age of patient, and day of week, is there any evidence of differential complication outcomes depending on time of day of ER encounter?

```{r}
surgery_updated_1<-surgery_updated%>%
  mutate(complication_number = ifelse(complication=="No",0,1))

  surgery_updated_1
```

```{r}
#logistic regression 
#significance value for time of day 

complication_model <- glm(complication_number ~ age + hospital + dow + hours_from_6pm,
                       data = surgery_updated_1, 
                       family = "binomial")


complication_model
summary(complication_model)
```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
